# Field Specifications

This page gives the full specification for each field in the metalab dataset, including: required fields (which must be included for every MA), optional fields (which are only used for some MAs), and derived fields (which are computed by the site).

```{r a, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(htmltools)
library(magrittr)
library(shinydashboard)
library(shiny)
library(purrr)
library(DT)
library(here)
htmltools::tagList(
  rmarkdown::html_dependency_font_awesome(),
  rmarkdown::html_dependency_bootstrap(theme = "default"),
  rmarkdown::html_dependency_highlightjs(highlight = "default"))
##source(here("pages", "assets", "helpers.R"))
##htmltools::includeScript(here("pages", "assets", "custom.js"))
```

```{r b, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyr)

fields <- yaml::yaml.load_file(here("metadata", "spec.yaml"))
fields_derived <- yaml::yaml.load_file(here("metadata", "spec_derived.yaml")) %>%
  transpose() %>%
  simplify_all() %>%
  dplyr::as_data_frame()

get_property <- function(property, property_fun = function(x) x) {
    map_chr(fields, function(entry) {
      if (property %in% names(entry) && !is.null(entry[[property]]))
        property_fun(entry[[property]])
      else ""
    })
  }
  
process_options <- function(options) {
  if (class(options) == "list") {
    opts <- names(unlist(options, recursive = FALSE))
  } else {
    opts <- options
  }
  paste(map_chr(opts, ~sprintf("<code>%s</code>", .x)), collapse = ", ")
}

fields_data <- dplyr::data_frame(field = get_property("field"),
                          description = get_property("description"),
                          type = get_property("type"),
                          format = get_property("format"),
                          options = get_property("options", process_options),
                          required = get_property("required")) %>%
  tidyr::unite(`format/options`, format, options, sep = "") %>%
  split(.$required) %>%
  map(~.x %>% dplyr::select(-required))

make_datatable <- function(df) {
    DT::datatable(
      df,
      escape = FALSE,
      width = "100%",
      style = "bootstrap",
      rownames = FALSE,
      extensions = 'Buttons',
      options = list(scrollX = TRUE, autoWidth = TRUE, pageLength = 20)
    )
  }

req_table <- make_datatable(fields_data[["TRUE"]])
opt_table <- make_datatable(fields_data[["FALSE"]])
drv_table <- make_datatable(fields_derived)

```


## Required fields
`r req_table`

<!-- ## Optional fields -->
<!-- `r opt_table` -->

<!-- ## Derived fields -->
<!-- `r drv_table` -->

<script>
  $(window).on('hashchange', function() {
    if (window.location.hash.indexOf("field_specs") > 0) { window.location.reload(); }
  });
</script>

