---
header:
  caption: ""
  image: ""
title: Publications
view: 4
---

## Citation Policy 

MetaLab encourages researchers to use data available on its
website. For example, you can cite meta-analytic results, or download
datasets and and conduct custom analyses. Before using MetaLab data in
your publication, we ask that you please read our [citation
policy](/documentation/using_ma_data/citation_policy).

## Metalab meta-analyses
```{r include = FALSE}
library(dplyr)
library(purrr)
library(here)
library(metalabr)
library(readr) 

metalabr::load_cached_data(here::here('shinyapps', 'site_data', 'Rdata', 'metalab.Rdata')) 
filtered_dataset <- filter(dataset_info, full_citation != "") #only print the datasets that have full citations
filtered_dataset <- filtered_dataset[order(filtered_dataset$full_citation),]
```

```{r, echo=FALSE, results = "asis"} 

for(i in 1:nrow(filtered_dataset)) {
  cat(filtered_dataset$full_citation[i])
  if (filtered_dataset$link[i] != ""){
    cat(" [[Paper]](", filtered_dataset$link[i], ")")
  }
  cat('  \n\n')
}

```


## Publications that used existing MetaLab data

**Bergmann, C. Tsuji, S., & Cristia, A. (2017).** Top-down versus bottom-up theories of phonological acquisition: A big data approach. In: *Proceedings of Interspeech 2017*, pp. 2013–2016. DOI: 10.21437/Interspeech.2017-1443 [[Paper]](http://www.isca-speech.org/archive/Interspeech_2017/abstracts/1443.html)

**Bergmann, C., Tsuji, S., Piccinini, P.E., Lewis, M.L., Braginsky, M., Frank, M.C., & Cristia, A. (2018).** Promoting replicability in developmental research through meta-analyses: Insights from language acquisition research. *Child Development, 89*, 1996-2009 . DOI: 10.1111/cdev.13079 [[Repository]](https://osf.io/uhv3d/)

**Lewis, M. L., Braginsky, M., Tsuji, S., Bergmann, C., Piccinini, P. E., Cristia, A., & Frank, M. C. (2017/under review).** A Quantitative Synthesis of Early Language Acquisition Using Meta-Analysis. DOI: 10.17605/OSF.IO/HTSJM [[Preprint]](http://psyarxiv.com/htsjm) 

**Mathur, M. B., & VanderWeele, T. J. (2020).** Estimating Publication Bias in Meta‐Analyses of Peer‐Reviewed Studies: A Meta‐Meta‐Analysis Across Disciplines and Journal Tiers. *Research Synthesis Methods.* DOI: 10.1002/jrsm.1464 [[Paper]](https://onlinelibrary.wiley.com/doi/abs/10.1002/jrsm.1464)

**Mathur, M. B., & VanderWeele, T. J. (2020).** Sensitivity analysis for publication bias in meta‐analyses. *Journal of the Royal Statistical Society. Series C, Applied Statistics, 69*(5), 1091. DOI: 10.1111/rssc.12440 [[Paper]](https://rss.onlinelibrary.wiley.com/doi/pdf/10.1111/rssc.12440)

**Tsuji, S. & Cristia, A. (2017).** Which Acoustic and Phonological Factors Shape Infants’ Vowel Discrimination? Exploiting Natural Variation in InPhonDB. In: *Proceedings of Interspeech 2017*, pp. 2108-2112. DOI: 10.21437/Interspeech.2017-1468 [[Paper]](http://www.isca-speech.org/archive/Interspeech_2017/abstracts/1468.html)

**Tsuji, S., Cristia, A., Frank, M. C., & Bergmann, C. (2020).** Addressing Publication Bias in Meta-Analysis. *Zeitschrift für Psychologie, 228,* 50-61. DOI: 10.1027/2151-2604/a000393 [[Paper]](https://econtent.hogrefe.com/doi/abs/10.1027/2151-2604/a000393?journalCode=zfp)


