---
title: "Design Choice Analyses"
author: "Molly Lewis"
date: "`r Sys.Date()`"
summary: "The research question determines many design choices in developmental research -- e.g., is the hypothesis related to the timecourse of various pressures, or merely the presence of a bias? Some methods are better suited than others for answering these different questions."
output: 
  blogdown::html_page:
    self_contained: false
    toc: true
    highlight: tango
    fig.width: 8
    fig.height: 5
---
  
## Introduction
The research question determines many design choices in developmental research -- e.g., is the hypothesis related to the timecourse of various pressures, or merely the presence of a bias? Some methods are better suited than others for answering these different questions. But, design choices can also influence the _size_ of the effect: Some methods are less noisy than others, and therefore result in larger effects sizes. The size of the effect may further depend on the particular age of the child in a study, with some methods better suited to different age groups. Here we look across datasets in Metalab at four design choices -- method, response mode, depenedent measure, and experimental design -- and their relationship to effect sizes, and other variables of interest.

This report includes effect sizes for participants 60 months or younger.

```{r, setup, include=FALSE}
library(here)
library(ggplot2)
load(here("shinyapps", "site_data", "Rdata", "metalab.Rdata"))
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE)
#source("../dashboard/global.R", chdir = TRUE)
library(metafor)
#library(tidyverse)
library(dplyr)
library(tidyr)
library(stringr)
library(purrr)
library(langcog)
```

## Data available for each design choice variable
Method
```{r}
metalab_data <- metalab_data %>%
            filter(mean_age_months <= 60)

metalab_data$method = as.factor(metalab_data$method)
method.pd = metalab_data %>%
  group_by(method, dataset) %>%
  filter(n() > 3) %>%
  summarise(n = n())

ggplot(method.pd, aes(y = n, fill = dataset, x = method)) + 
         geom_bar(stat = "identity") +
         xlab("method") +
         ylab("N effect sizes") +
         theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
        guides(fill=guide_legend(ncol=2))
```

Response Mode
```{r}
metalab_data$response_mode = as.factor(metalab_data$response_mode)

response.pd = metalab_data %>%
  group_by(response_mode, dataset) %>%
  summarise(n = n())

ggplot(response.pd, aes(y = n, fill = dataset, x = response_mode)) + 
         geom_bar(stat = "identity") +
         xlab("response mode") +
         ylab("N effect sizes") +
  theme (axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
        guides(fill=guide_legend(ncol=2))
```

Dependent Measure
```{r}
metalab_data$dependent_measure= as.factor(metalab_data$dependent_measure)
dm.pd = metalab_data %>%
  group_by(dependent_measure, dataset) %>%
  summarise(n = n())

ggplot(dm.pd, aes(y = n, fill = dataset, x = dependent_measure)) + 
         geom_bar(stat = "identity") +
         xlab("method") +
         ylab("N effect sizes") +
         theme (axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
        guides(fill=guide_legend(ncol=2))
```

Participant design
```{r}
metalab_data$participant_design = as.factor(metalab_data$participant_design)
participant_design.pd = metalab_data %>%
  group_by(participant_design, dataset) %>%
  summarise(n = n())

ggplot(participant_design.pd, aes(y = n, fill = dataset, x = participant_design)) + 
         geom_bar(stat = "identity") +
         xlab("participant design") +
         ylab("N effect sizes") +
      theme (axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) + 
        guides(fill=guide_legend(ncol=2))
```

## Design choice  variables by age
```{r} 
age.response_mode.pd = metalab_data %>%
  mutate(mean_age_months_rounded = cut_width(mean_age_months,  width = 3, boundary = 0))  %>%
  group_by(mean_age_months_rounded, response_mode) %>%
  summarise(n = n()) %>%
  mutate(prop = n / sum(n))

ggplot(age.response_mode.pd, aes(x = mean_age_months_rounded, y = prop, color = response_mode)) +
  geom_point() +
  geom_line(aes(group = response_mode)) +
    xlab("Age (months)") +
  theme (axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  ggtitle("Response Mode")

ggplot(age.response_mode.pd, aes(x = mean_age_months_rounded, y = n, color = response_mode)) +
  geom_point() +
  geom_line(aes(group = response_mode)) +
    xlab("Age (months)") +
  theme (axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  ggtitle("Response Mode")

age.method.pd = metalab_data %>%
  mutate(mean_age_months_rounded = cut_width(mean_age_months,  width = 3, boundary = 0))  %>%
  group_by(mean_age_months_rounded, method) %>%
  summarise(n = n()) %>%
  mutate(prop = n / sum(n))

ggplot(age.method.pd, aes(x = mean_age_months_rounded, y = prop, color = method)) +
  geom_point() +
  geom_line(aes(group = method)) +
    xlab("Age (months)") +
  theme (axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  ggtitle("Method")

ggplot(age.method.pd, aes(x = mean_age_months_rounded, y = n, color = method)) +
  geom_point() +
  geom_line(aes(group = method)) +
    xlab("Age (months)") +
  theme (axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  ggtitle("Method")

age.dm.pd = metalab_data %>%
  mutate(mean_age_months_rounded = cut_width(mean_age_months,  width = 3, boundary = 0))  %>%
  group_by(mean_age_months_rounded, dependent_measure) %>%
  summarise(n = n()) %>%
  mutate(prop = n / sum(n))

ggplot(age.dm.pd, aes(x = mean_age_months_rounded, y = prop, color = dependent_measure)) +
  geom_point() +
  geom_line(aes(group = dependent_measure)) +
    xlab("Age (months)") +
  theme (axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  ggtitle("Dependent Measure")

ggplot(age.dm.pd, aes(x = mean_age_months_rounded, y = n, color = dependent_measure)) +
  geom_point() +
  geom_line(aes(group = dependent_measure)) +
    xlab("Age (months)") +
  theme (axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  ggtitle("Dependent Measure")

age.pd.pd = metalab_data %>%
  mutate(mean_age_months_rounded = cut_width(mean_age_months,  width = 3, boundary = 0))  %>%
  group_by(mean_age_months_rounded, participant_design) %>%
  summarise(n = n()) %>%
  mutate(prop = n / sum(n))

ggplot(age.pd.pd, aes(x = mean_age_months_rounded, y = prop, color = participant_design)) +
  geom_point() +
  geom_line(aes(group = participant_design)) +
  xlab("Age (months)") +
  theme (axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  ggtitle("Participant Design")

ggplot(age.pd.pd, aes(x = mean_age_months_rounded, y = n, color = participant_design)) +
  geom_point() +
  geom_line(aes(group = participant_design)) +
    xlab("Age (months)") +
  theme (axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  ggtitle("Participant Design")
```

## Effect size by design choice variables

### By dataset
Get residual effect size, controling for age and phenonmenon
```{r}
full.model = rma(d_calc ~ dataset + mean_age_1, 
        vi = d_var_calc, data = metalab_data, method = "REML")

residuals = rstandard(full.model)

metalab_data = metalab_data %>%
            bind_cols(as.data.frame(residuals$resid),
                      as.data.frame(residuals$z)) %>%
            rename(residual.d = `residuals$resid`, 
                   residual.d.s = `residuals$z`) # standardized
```

```{r, fig.width = 10}
method.pd = metalab_data %>%
  group_by(method, dataset) %>%
  summarise(residual.d = mean(residual.d),
            n = n())

ggplot(method.pd, aes(x = method, y = residual.d, color = dataset)) +
  geom_point(aes(size = n)) +
  geom_line(aes(group = dataset)) + 
  theme (axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  ggtitle("Method") +
  guides(colour=guide_legend(ncol=2))

response.pd = metalab_data %>%
  group_by(response_mode, dataset) %>%
  summarise(residual.d = mean(residual.d),
            n = n())

ggplot(response.pd, aes(x = response_mode, y = residual.d, color = dataset)) +
  geom_point(aes(size = n)) +
  geom_line(aes(group = dataset)) + 
  theme (axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  ggtitle("Response Mode") +
  guides(colour=guide_legend(ncol=2))

dm.pd = metalab_data %>%
  group_by(dependent_measure, dataset) %>%
  summarise(residual.d = mean(residual.d),
            n = n())

ggplot(dm.pd, aes(x = dependent_measure, y = residual.d, color = dataset)) +
  geom_point(aes(size = n)) +
  geom_line(aes(group = dataset)) + 
  theme (axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  ggtitle("Dependent Measure") +
  guides(colour=guide_legend(ncol=2))

participant_design.pd = metalab_data %>%
  group_by(participant_design, dataset) %>%
  summarise(residual.d = mean(residual.d),
            n = n())

ggplot(participant_design.pd, aes(x = participant_design, y = residual.d, color = dataset)) +
  geom_point(aes(size = n)) +
  geom_line(aes(group = dataset)) + 
  theme (axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  ggtitle("Participant Design") +
  guides(colour=guide_legend(ncol=2))
```

### Across datasets
```{r}
method.pd.all = metalab_data %>%
  group_by(method) %>%
  multi_boot_standard(col = "residual.d") %>%
  ungroup() %>%
  mutate(method = reorder(method, mean))

ggplot(method.pd.all, aes(x = method, y = mean, fill = method)) +
  geom_bar(position="dodge", stat="identity") +  
  geom_errorbar(aes(ymin = ci_lower, ymax= ci_upper), 
                width=0.2, position="dodge") +
  ylab("residual effect size") +
  xlab("method") +
  theme(legend.position="none") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) 

response.pd.all = metalab_data %>%
  group_by(response_mode) %>%
  multi_boot_standard(col = "residual.d") %>%
  ungroup() %>%
  mutate(response_mode = reorder(response_mode, mean)) 

ggplot(response.pd.all, aes(x = response_mode, y = mean, fill = response_mode)) +
  geom_bar(position="dodge", stat="identity") +  
  geom_errorbar(aes(ymin = ci_lower, ymax= ci_upper), 
                width=0.2, position="dodge") +
  ylab("residual effect size") +
  xlab("response mode") +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) 

dm.pd.all = metalab_data %>%
  group_by(dependent_measure) %>%
  multi_boot_standard(col = "residual.d") %>%
    ungroup() %>%
  mutate(dependent_measure = reorder(dependent_measure, mean))

ggplot(dm.pd.all, aes(x =dependent_measure, y = mean, fill = dependent_measure)) +
  geom_bar(position="dodge", stat="identity") +  
  geom_errorbar(aes(ymin = ci_lower, ymax= ci_upper), 
                width=0.2, position="dodge") +
  ylab("residual effect size") +
  xlab("dependent measure") +
  theme(legend.position="none") +
  theme (axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) 

participant_design.pd.all = metalab_data %>%
  group_by(participant_design) %>%
  multi_boot_standard(col = "residual.d") %>%
  ungroup() %>%
  mutate(participant_design = reorder(participant_design, mean))

ggplot(participant_design.pd.all, 
       aes(x = participant_design, y = mean, fill = participant_design)) +
  geom_bar(position="dodge", stat="identity") +  
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), 
                width=0.2, position="dodge") +
  ylab("residual effect size") +
  xlab("participant design") +
  theme(legend.position="none") +
  theme (axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) 
```
