---
title: "Research Networks"
author: "Molly Lewis"
date: "`r Sys.Date()`"
output:
  html_document:
    highlight: tango
    theme: united
code_folding: hide
---
  
SUMMARY: Looking at number of citations as DV, papers with bigger effects sizes are not cited more, but papers with bigger ns are cited more. Open access-ness is related to number of citations, and maybe n and d.

```{r, setup, include = FALSE}
library(knitr)
library(tidyr)
library(langcog)
library(rcrossref)
library(tidyverse)
library(stringr)
library(lme4)

# load data
knitr::opts_chunk$set(fig.width = 8, fig.height = 5, echo = TRUE,
                      warning = FALSE, message = FALSE, cache = FALSE)
ggplot2::theme_set(langcog::theme_mikabr(base_family = "Ubuntu"))
```

Get all dois
(Obtained from: https://apps.crossref.org/SimpleTextQuery/ (copy-pasting 50 at a time))
```{r}
dois <- read.csv("dois2.csv") %>%
      select(study_ID, doi) %>%
      filter(doi != "" & !is.na(doi)) %>%
      mutate(doi = ifelse(grepl(".org/", doi),
                          unlist(lapply(str_split(doi, ".org/"), 
                                   function(x) {x[2]})), as.character(doi))) %>%
      as_data_frame()
```

Get doi metadata
(Using rcrossref pacage)
```{r}
doi.data = dois %>%
    group_by(study_ID) %>%
    do(reference.count = cr_works(dois = .$doi)$data$reference.count,
     date = cr_works(dois = .$doi)$data$created,
     doi = cr_works(dois = .$doi)$data$DOI) %>%
     unnest() 
```

Merge metadata in ES dataframe
```{r}
# merge in dois to df
all_data = left_join(all_data, doi.data, by = "study_ID")  %>%
           mutate(reference.count = as.numeric(reference.count),
           date = unlist(lapply(str_split(date, "-"), 
                                   function(x) {x[1]})))
```

## Domain-level analyses
```{r}
domain.references = all_data %>%
  group_by(short_name) %>%
  multi_boot_standard(column = "reference.count", na.rm =T)

ggplot(domain.references, aes(x = reorder(short_name,mean) ,y = mean, fill = short_name)) +
  xlab("phenomenon") +
  ylab("mean number of citations") +
  geom_bar(stat ="identity") +
  geom_linerange(aes(ymax = ci_upper, ymin = ci_lower)) +
  theme_bw() +
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 90, hjust = 1))
```

## Method-level analyses
```{r}
method.references = all_data %>%
  group_by(method) %>%
  multi_boot_standard(column = "reference.count", na.rm =T)

ggplot(method.references, aes(x = reorder(method,mean) ,y = mean, fill = method)) +
  xlab("method") +
  ylab("mean number of citations") +
  geom_bar(stat ="identity") +
  geom_linerange(aes(ymax = ci_upper, ymin = ci_lower)) +
  theme_bw() +
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 90, hjust = 1))

summary(lmer(reference.count ~ method + as.numeric(date) + (1|dataset) , data = all_data))
```

## Method-level analyses
```{r}
response.references = all_data %>%
  group_by(response_mode) %>%
  multi_boot_standard(column = "reference.count", na.rm =T)

ggplot(response.references, aes(x = reorder(response_mode,mean) ,y = mean, fill = response_mode)) +
  xlab("response mode") +
  ylab("mean number of citations") +
  geom_bar(stat ="identity") +
  geom_linerange(aes(ymax = ci_upper, ymin = ci_lower)) +
  theme_bw() +
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 90, hjust = 1))

summary(lmer(reference.count ~ response_mode + as.numeric(date) + (1|dataset) , data = all_data))
```

No interpretable differences for response mode.

## Paper-level analyses

Papers with bigger effect sizes do not get cited more (controlling for year)
```{r}
paper.data = all_data %>%
  group_by(doi.x,short_cite) %>%
  summarize(d_calc = mean(d_calc, na.rm = T),
            reference.count = reference.count[1],
            date = as.numeric(date)[1],
            dataset = dataset[1], 
            n = sum(n_1, na.rm = T) + sum(n_2, na.rm = T) )

summary(lm(reference.count ~ d_calc + as.numeric(date) + dataset , d = paper.data))

summary(lmer(reference.count ~ d_calc + as.numeric(date) + (1|dataset) , data = paper.data))

ggplot(filter(paper.data, !is.na(date)), 
       aes(y = reference.count, x = d_calc)) +
  geom_point(aes(color = dataset)) +
  geom_smooth(method = "lm") +
  facet_wrap(~date, scales = "free") +
  theme_bw() +
  theme(legend.position = "none")

```

No difference if you take absolute effect size.

```{r}
ggplot(filter(paper.data, !is.na(date)), 
       aes(y = reference.count, x = n)) +
  geom_point(aes(color = dataset)) +
  geom_smooth(method = "lm") +
  facet_wrap(~date, scales = "free") +
  theme_bw() +
  theme(legend.position = "none")

summary(lm(reference.count ~ n + as.numeric(date) + dataset , d = paper.data))

summary(lmer(reference.count ~ n + as.numeric(date) + (1|dataset) , data = paper.data))
```

However, papers with more participants ARE cited more.

TO DO:
- look at measures of bias and number of citation - are citaitons sensitive to bias in the literatuer?
- look at network level features - are these correlated with bias at the domain level and effect size at the paper level? 
- for each paper, get all authors, for each atuhor, get all authors of all other papers they've co-authored. Add link if two authors have writtedn a paper together. Do papers with bigger ES have more diverse network?


### looking at open access status
```{r}
library(roadoi)

doi.meta = roadoi::oadoi_fetch(dois = c(dois$doi), 
                    email = "mollyllewis@gmail.com")

doi.meta.paper = doi.meta %>%
 # select(-green_base_collections, -open_urls, -open_base_ids,
  #       -reported_noncompliant_copies) %>%
  mutate_each(funs(factor),c(-year,-is_subscription_journal,
                             -is_free_to_read,-is_boai_license,
                             -free_fulltext_url, -found_green, -found_hybrid))%>%
  left_join(paper.data, by = c("doi" ="doi.x"))

doi.meta.paper %>%
  group_by(is_free_to_read) %>%
  summarize(n = n()) %>%
  kable()

doi.meta.paper %>%
  group_by(is_free_to_read, dataset) %>%
  summarize(n = n()) %>%
  kable()

citation.data = doi.meta.paper %>%
  select(is_free_to_read, n, reference.count, d_calc) %>%
  gather("measure", "value", -1) %>%
  group_by(is_free_to_read, measure)  %>%
  multi_boot_standard(column = "value", na.rm = T)
  
ggplot(citation.data, aes(x = is_free_to_read ,y = mean, fill = measure)) +
  geom_bar(stat ="identity") +
  facet_wrap(~measure, scales = "free") +
  geom_linerange(aes(ymax = ci_upper, ymin = ci_lower)) +
  theme_bw() +
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 90, hjust = 1))

doi.meta.es = doi.meta %>%
  mutate_each(funs(factor),c(-year,-is_subscription_journal,
                             -is_free_to_read,-is_boai_license,
                             -free_fulltext_url, -found_green, -found_hybrid))%>%
  select(-dataset, -d_calc, -n, -reference.count) %>%
  left_join(all_data, by = c("doi" ="doi"))

summary(lmer(d_calc~ is_free_to_read + (1|dataset) ,data = doi.meta.es))
summary(lmer(reference.count ~ is_free_to_read + (1|dataset) ,data = doi.meta.es))
summary(lmer(n ~ is_free_to_read + year + (1|dataset) ,data = doi.meta.es))

```
Papers in open access journals are cited more often. Depending on the analysis, they also have bigger ns and smaller ds.

### Web of science
```{r}
string = ""
for (i in 1:length(dois$doi)) {
  string = paste(string, dois$doi[i], sep = " OR ")
}

## search web of science-> save to marked list -> download marked list as .txt
library(bibliometrix) 

D <- readFiles("savedrecs (3).txt")
M <- convert2df(D, dbsource = "isi", format = "plaintext")
```

WOS analyses
```{r}
biblioAnalysis(M, sep = ";") %>%
  summary(k = 10, pause = FALSE) 

allWOS = inner_join(paper.data, M, by = c("doi.x" = "DI"))

results <- biblioAnalysis(allWOS, sep = ";")

NetMatrix <- biblioNetwork(M, analysis = "co-citation", network = "authors", sep = "; ")
networkPlot(NetMatrix, Title = "Authors' co-citations", n = 20)

NetMatrix <- biblioNetwork(M, analysis = "co-citation", network = "references", sep = "; ")
networkPlot(NetMatrix, Title = "References' co-citations", n = 20)

NetMatrix <- biblioNetwork(M, analysis = "coupling", network = "authors", sep = "; ")
networkPlot(NetMatrix, Title = "Authors' Coupling", n = 20)

NetMatrix <- biblioNetwork(M, analysis = "coupling", 
                           network = "references", sep = "; ")
networkPlot(NetMatrix, Title = "Manuscript Coupling", n = 30)

NetMatrix <- biblioNetwork(M, analysis = "collaboration", 
                           network = "authors", sep = "; ")
networkPlot(NetMatrix, Title = "Author collaboration", n = 30)

NetMatrix <- biblioNetwork(M, analysis = "co-occurrences", 
                           network = "authors", sep = "; ")
networkPlot(NetMatrix, Title = "Author co-occurences", n = 30)

NetMatrix <- biblioNetwork(M, analysis = "co-occurrences", 
                           network = "keywords", sep = "; ")
networkPlot(NetMatrix, Title = "keywords co-occurences", n = 30)

```

```{r}


CR <- citations(M, field = "article", sep = ".  ")

CR$Cited[1:10]

CR <- citations(M, field = "author", sep = ".  ")

CR$Cited[1:10]

CR <- localCitations(M, results, sep = ".  ")

CR[1:10]

DF <- dominance(results, k = 10)
DF

indices <- Hindex(M, authors="FERNALD A", sep = ";")
indices
indices$CitationList

A <- cocMatrix(M, Field = "AU", sep = ";")

NetMatrix <- biblioNetwork(M, analysis = "collaboration", network = "authors", sep = ";")
 S <- couplingSimilarity(NetMatrix, type="jaccard")
 
 net=networkPlot(S, n = 20, Title = "Authors' Coupling", type = "fruchterman", size=FALSE,remove.multiple=TRUE)
 
 networkPlot(NetMatrix, n =100, Title = "Country Collaboration", type = "circle", size=TRUE, remove.multiple=FALSE)
 
 NetMatrix <- biblioNetwork(M, analysis = "co-citation", network = "references", sep = ".  ")

# Plot the network
net=networkPlot(NetMatrix, n = 15, Title = "Co-Citation Network", type = "fruchterman", size=T, remove.multiple=FALSE)


NetMatrix <- biblioNetwork(M, analysis = "co-occurrences", network = "keywords", sep = ";")

# Plot the network
net=networkPlot(NetMatrix, n = 20, Title = "Keyword Co-occurrences", type = "kamada", size=T)

CS <- conceptualStructure(M,field="ID", minDegree=4, k.max=5, stemming=FALSE)


histResults <- histNetwork(M, n = 15, sep = ".  ")

# Plot a historical co-citation network
net <- histPlot(histResults, size = FALSE)







```
