
```{r child='assets/setup.Rmd'}
```

```{r echo=FALSE}
menuNavbar()
```

# Frequently Asked Questions

### Contributing to MetaLab

#### How can I contribute to the database?

### About MetaLab 

#### I’ve used the database for an analysis that I’m writing up. How do I cite it?


#### What is the license for derivative works from Wordbank (e.g., graphs generated by the site)?

Unless otherwise stated, MetaLab and its datasets are licensed under
a Creative Commons Attribution 4.0 International License, CC BY
4.0. If you use MetaLab in a derivative work, you must give credit,
but otherwise you are free to do anything else you want with most
products from the site.  Some datasets listed under the Contributors
page may be marked with a CC BY NC License 4.0 logo. This means these
particular datasets are licensed under a Creative Commons
Attribution-NonCommercial 4.0 International License, CC BY-NC
4.0. These datasets may not be used for commercial purposes but
otherwise are free to use and adapt as long as credit is given.

#### How did you build MetaLab?

MetaLab is written almost entirely in R, using a combination of
RMarkdown and Shiny.

#### Who funds MetaLab?


```{r, echo=FALSE}
htmltools::includeHTML("footer.html")
```
