
```{r child='assets/setup.Rmd'}
```

```{r echo=FALSE}
menuNavbar()
```

1. Researchers publishing or presenting work using data in MetaLab must cite the publications linked to that dataset, as shown on the documentation page for the individual dataset. (If there is no linked citation, then no citation for the individual dataset is necessary).

2. For tracking use of the database and its affiliated tools, please also cite: Bergmann, C., Tsuji, S., Piccinini, P.E., Lewis, M.L., Braginsky, M., Frank, M.C., & Cristia, A. (2017). Promoting replicability in developmental research through meta-analyses: Insights from language acquisition research (Submitted).

3. If researchers use more than five datasets, we ask users as a courtesy to cite all data. But in case of severe space limitations, the database as a whole alone may be cited.

4. Since the MetaLab site is dynamic, we recommend that you list the date of download for your data in your manuscript. For example: "We analyze all data currently in MetaLab (Bergmann et al., 2017). Data were downloaded on 06/17/17."

## {.tabset .nav-tabs-custom}

### Publications on MetaLab

Frank, M. C., Braginsky, M., Yurovsky, D., & Marchman, V. A. (2016). **Wordbank: An open repository for developmental vocabulary data**. Journal of Child Language. [[pdf]](http://langcog.stanford.edu/papers_new/frank-2016-jcl.pdf)

### Dataset Publications

Dataset Publications (you can write in markdown here)

### Publications using MetaLab

Publications using MetaLab (you can write in markdown here)
