```{r child='assets/setup.Rmd'}
```

```{r echo=FALSE}
menuNavbar()
```

<div style="margin-left:200px; margin-right:200px; margin-top:30px; font-size:16px">

MetaLab allows researchers to use data available on its website. This can be by citing meta-analytic results, or downloading dataset and conducting custom analyses. In both cases our citation policy is the following:

1. Researchers publishing or presenting work using data in MetaLab must cite the publications linked to that dataset, as listed in the [Documentation](https://langcog.github.io/metalab2/documentation.html#datasets). (If there is no citation, then no citation for the individual dataset is necessary).

2. For tracking use of MetaLab, please also cite at least one of the following:    
    * Bergmann, C., Tsuji, S., Piccinini, P.E., Lewis, M.L., Braginsky, M., Frank, M.C., & Cristia, A. (2018). Promoting replicability in developmental research through meta-analyses: Insights from language acquisition research. *Child Development, 89*, 1996-2009 . DOI: 10.1111/cdev.13079 [[Repository]](https://osf.io/uhv3d/)

    * Lewis, M. L., Braginsky, M., Tsuji, S., Bergmann, C., Piccinini, P. E., Cristia, A., & Frank, M. C. (2017/under review). A Quantitative Synthesis of Early Language Acquisition Using Meta-Analysis. DOI: 10.17605/OSF.IO/HTSJM [[Preprint]](http://psyarxiv.com/htsjm) 

3. If researchers use more than five datasets, we ask users as a courtesy to cite all data. But in case of severe space limitations, the database as a whole alone may be cited.

4. Since the MetaLab site is dynamic, we recommend that you list the date of download for your data in your manuscript. For example: "We analyze all data currently in MetaLab (Bergmann et al., 2017). Data were downloaded on 06/17/17."

</div>

<!--- "section" is ID of div containing tabs below -->
<style>
#section {
  margin-left:200px;
  margin-right:200px;
  font-size:16px;
}
</style>

## {.tabset .nav-tabs-custom}

### Publications on MetaLab

Bergmann, C., Tsuji, S., Piccinini, P.E., Lewis, M.L., Braginsky, M., Frank, M.C., & Cristia, A. (2018). Promoting replicability in developmental research through meta-analyses: Insights from language acquisition research. *Child Development, 89*, 1996-2009 . DOI: 10.1111/cdev.13079 [[Repository]](https://osf.io/uhv3d/)

Lewis, M. L., Braginsky, M., Tsuji, S., Bergmann, C., Piccinini, P. E., Cristia, A., & Frank, M. C. (2017/under review). A Quantitative Synthesis of Early Language Acquisition Using Meta-Analysis. DOI: 10.17605/OSF.IO/HTSJM [[Preprint]](http://psyarxiv.com/htsjm) 

### Publications using MetaLab

Tsuji, S. & Cristia, A. (2017). Which Acoustic and Phonological Factors Shape Infants’ Vowel Discrimination? Exploiting Natural Variation in InPhonDB. In: *Proceedings of Interspeech 2017*, pp. 2108-2112. DOI: 10.21437/Interspeech.2017-1468 [[Paper]](http://www.isca-speech.org/archive/Interspeech_2017/abstracts/1468.html)

Bergmann, C. Tsuji, S., & Cristia, A. (2017). Top-down versus bottom-up theories of phonological acquisition: A big data approach. In: *Proceedings of Interspeech 2017*, pp. 2013–2016. DOI: 10.21437/Interspeech.2017-1443 [[Paper]](http://www.isca-speech.org/archive/Interspeech_2017/abstracts/1443.html)
