---
title: "Developmental curves"
author: "Michael Frank"
date: "Last updated on `r Sys.Date()`."
---

```{r, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
#ggplot2::theme_set(langcog::theme_mikabr(base_family = "Ubuntu"))
#source("../OLD/dashboard/global.R", chdir = TRUE)
library(knitr)
library(tidyverse)
library(lme4)
library(broom)
library(metafor)
library(RColorBrewer)
library(here)
library(brms)
source(here("shinyapps/common/global.R"), chdir = TRUE)

```

# Introduction

Trying to pick back up the question of how different developmental phenomnena relate to one another and how they change over time. 

Open questions:
1. is growth (in ES) logarithmic, exponential, linear, etc.? 
2. are phenomena all growing from the same zero point or are there offsets (e.g., do somethings "start" later or does all learning start at birth)

Methodological idea: use bayesian meta-regression and model comparison to try and model ES across phenomena.

Confounds:
* selection of harder/easier studies across papers - need to look potentially at within-paper slopes
* method confounds - need to control for this
* need to remove MAs that don't represent real phenomena - major judgment call here

Might want to limit to early language for now? Also could consider limiting to 0-36 or 0-48 months just because things blow up after that and data are sometimes sparse.

# Exploration 

Data with curves by phenomenon. 

```{r}
filter(metalab_data, 
       domain == "early_language", 
       mean_age_months < 36) %>%
  ggplot(aes(x = mean_age_months, y = d_calc, 
             weight = 1/d_var_calc)) +
  geom_point(aes(size = 1/d_var_calc),
             alpha = .3) + 
  geom_smooth(method="lm", formula = y ~ x, 
              aes(col = "Linear"), 
              se = FALSE) + 
  geom_smooth(method="lm", formula = y ~ log(x), 
              aes(col = "Log"),
              se = FALSE) + 
  geom_smooth(method="lm", formula = y ~ I(x^2),
              aes(col = "Quadratic"),
              se = FALSE) +
  facet_wrap(~ short_name) + 
  geom_hline(yintercept = 0, lty = 2, col = "black") + 
  xlab("Mean age (months)") +
  ylab("Effect size (d)") +
  scale_colour_solarized(name="Models", breaks = c("Linear", "Log",
                                                "Quadratic", "Linear and Log"),
                                     labels=c("Linear" = "Linear",
                                              "Log" = "Log",
                                              "Quadratic" = "Quadratic",
                                              "Linear and Log" = "Linear and Log")) +
  ggthemes::theme_few()
```

# Try Bayesian MA on IDS preference

Note, pulling heavily from:
* https://solomonkurz.netlify.app/post/bayesian-meta-analysis/
* https://vuorre.netlify.app/post/2016/09/29/meta-analysis-is-a-special-case-of-bayesian-multilevel-modeling/

Not sure why brms uses SE rather than variance, but we can do that. 

Try just one phenomenon. 

```{r}
idspref <- filter(d, short_name == "idspref")
```

First with variances. 

```{r}
rma(data = idspref, yi = d_calc, vi = d_var_calc, slab = short_cite) 
```

Next with SE just as a sanity check (turns out SE is sqrt(var) for sampling variances, I should have known this). 

```{r}
rma(data = idspref, yi = d_calc, sei = d_se_calc, slab = short_cite)
```

Fit the Bayesian version

```{r}
idspref_bayes <- 
  brm(data = idspref, 
      family = gaussian,
      d_calc | se(d_se_calc) ~ 1 + (1 | short_cite),
      prior = c(prior(normal(0, 1), class = Intercept),
                prior(cauchy(0, 1), class = sd)),
      iter = 2000, warmup = 1000, cores = 4, chains = 4,
      seed = 14)
idspref_bayes
```

# Full model


```{r}
d <- filter(metalab_data, 
       domain == "early_language") %>%
  mutate(d_se_calc = sqrt(d_var_calc)) %>%
  select(short_cite, short_name, d_calc, d_se_calc, method, mean_age_months) 
```


```{r}
alldata_bayes <- 
  brm(data = d, 
      family = gaussian,
      d_calc | se(d_se_calc) ~ mean_age_months 
                                + (mean_age_months | short_cite) 
                                + (mean_age_months | short_name),
      prior = c(prior(normal(0, 1), class = Intercept),
                prior(cauchy(0, 1), class = sd)),
      iter = 5000, warmup = 2000, cores = 4, chains = 4,
      seed = 14)
```

